High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-06-10 paper/main.tex
minor typo corrections, recompiled diffs

When the correlation dynamics were unstructured in time
(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
narrow) performed best.  This is because, when every timepoint's
correlations are independent of the correlations at every other
timepoint, averaging data over time dilutes the available signal.
Following a similar pattern, holding kernel shape fixed, narrower
kernel parameters better recovered randomly varying correlations.

@@

Overall, we found that we could reliably recover both first-order and
second-order correlations from the synthetic data
(Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
for longer intervals, or changed gradually (constant, ramping, and
event datasets), recovery performance was relatively high, and we were
better able to recover dynamic first-order correlations than
second-order correlations.  This is because errors in our \textit{estimation}
procedure at lower orders necessarily propagate to higher orders
(since lower-order correlations are used to estimate higher-order
correlations).  Conversely, when the correlations were particularly
\textit{un}stable (random datasets), we better recovered second-order
correlations.  This is because noises in our \textit{data generation}
procedure propagates from higher orders to lower orders (see
\textit{Synthetic data: simulating dynamic high-order correlations}).

>>>>

When the correlation dynamics were unstructured in time
(Fig.~\ref{fig:synthetic}b), a Dirac $\delta$ kernel (infinitely
narrow) performed best.  This is because, when every timepoint's
correlations are independent from the correlations at every other
timepoint, averaging data over time dilutes the available signal.
Following a similar pattern, holding kernel shape fixed, narrower
kernel parameters better recovered randomly varying correlations.

@@

Overall, we found that we could reliably recover both first-order and
second-order correlations from the synthetic data
(Fig.~\ref{fig:higher_order_sims}).  When the correlations were stable
for longer intervals, or changed gradually (constant, ramping, and
event datasets), recovery performance was relatively high, and we were
better able to recover dynamic first-order correlations than
second-order correlations.  This is because errors in our \textit{estimation}
procedure at lower orders necessarily propagate to higher orders
(since lower-order correlations are used to estimate higher-order
correlations).  Conversely, when the correlations were particularly
\textit{un}stable (random datasets), we better recovered second-order
correlations.  This is because noise in our \textit{data generation}
procedure propagates from higher orders to lower orders (see
\textit{Synthetic data: simulating dynamic high-order correlations}).
